---
title: "Working with API"
output: html_notebook
---

# Packages needed for working with API

```{r}
#install.packages(c("httr", "jsonlite"))

library(httr)
library(jsonlite)
```

# To fetch the data from API we need to build an API URL.

THE API KEY IS A SECRET. IT CANNOT BE USED ANYWHERE IN CODE DIRECTLY. 
Instead create a .Renviron file in your local repository with environmental variable API_KEY that you will reference in code. 

```
API_KEY=<your_api_key_value>
```
After you do this, save the changes to the .Renviron file and use CTRL+SHIFT+F10 to restart R session.

```{r}
# Set the base URL for the Last.fm API
base_url <- "http://ws.audioscrobbler.com/2.0/"

# Define the API method you want to use
api_method <- "method=artist.getTopTracks"

# API key referenced from enviromental variables
api_key <- Sys.getenv("API_KEY")

# Define the artist you want to get top tracks for
artist <- "Coldplay"

# Build the URL for the API request
api_url <- paste0(base_url, "?", api_method, "&artist=", URLencode(artist), "&api_key=", api_key, "&format=json")

# Send the API request
response <- GET(api_url)

# Check the status code of the response
status_code <- response$status_code

# Get the JSON content from the response
content <- content(response, "text", encoding = "UTF-8")

# Print JSON
#cat(content)

#transform it to Dataframe

df <- fromJSON(content)
df
```

